Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-29 FinalPaper/paper.tex
small compilation error

\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP M(H) for a smaller horizon h.  Incrementally solving the sequence M(1), M(2) forms the basis of LR\textsuperscript{2}TDP. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value h' for which already a heuristic value V is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1). The max-reward computation relies on knowing the maximum \textsubscriptreward any action can yield in any state or an upper bound on it.

@@

>>>>

\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP M(H) for a smaller horizon h.  Incrementally solving the sequence M(1), M(2) forms the basis of LR\textsuperscript{2}TDP. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value h' for which already a heuristic value V is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1). The max-reward computation relies on knowing the maximum R\textsubscript{max} any action can yield in any state or an upper bound on it.

@@

\subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}
